Measuring Hash Trustworthiness via Collision Utility Metrics: Logical Cryptanalysis of MD4

### 2017-12-05 dsn-2018/bare_conf.tex
Family similarity
Signed-off-by: Alexander Scheel <alexander.m.scheel@gmail.com>

A \textit{collision}, $L \subseteq \mathcal{I}$ is a subset of the
input space of a hash function with $\big|L\big| \geq 2$, such that
there exists an output $v \in S$ such that for all inputs $i \in L$,
$h(i) = c$. We extend this to arbitrary round hash functions using
the notation $(r, L)$, to explicitly denote that $L$ is a collision
under $h_{r}$.

\begin{itemize}
\item We define a \textit{multicollision} to be a collision which
  has multiple input states which hash to the same output under
  a single input block. That is, if $L$ is a collision, then
  $\forall i \in L$, $i_b = c$ for some $c \ in B$ for $L$ to be
  a multicollision.
\end{itemize}

For a simple collision, we say that the \textit{differential path}
is the difference between the two sets of intermediate state
variables. This is formally represented by an ordered tuple of
$r$ elements. We use the simple xor difference throughout this paper.

@@

From an intuitive standpoint, what this says is that collisions have
witnesses for their existence in reduced round versions of the function, and
further, that it is sufficient to search reduced round versions to find
candidates for extension into additional rounds. This likely derives from
the iterative construction of MD4 and the particular choice of block schedule.

\textbf{TODO -- Empirical justification / graphical representation?}

>>>>

A \textit{collision}, $L \subseteq \mathcal{I}$ is a subset of the
input space of a hash function with $\big|L\big| = 2$, such that
there exists an output $v \in S$ such that for all inputs $i \in L$,
$h(i) = c$. We extend this to arbitrary round hash functions using
the notation $(r, L)$, to explicitly denote that $L$ is a collision
under $h_{r}$.

\begin{itemize}
\item We define a \textit{multicollision} to be a collision which
  has multiple input states which hash to the same output under
  a single input block. That is, if $L$ is a collision, then
  $\forall i \in L$, $i_b = c$ for some $c \in B$ for $L$ to be
  a multicollision.
\end{itemize}

For a collision, we say that the \textit{differential path}
is the difference between the two sets of intermediate state
variables. This is formally represented by an ordered tuple of
$r$ elements. We use the simple xor difference throughout this paper.

@@

From an intuitive standpoint, what this says is that collisions have
witnesses for their existence in reduced round versions of the function, and
further, that it is sufficient to search reduced round versions to find
candidates for extension into additional rounds. This likely derives from
the iterative construction of MD4 and the particular choice of block schedule.
We present Figure \ref{Fig:PrecSim} as an example of the lattice structure
induced under $\precsim$ for example collision families.

\begin{figure*}
\begin{center}
\includegraphics[width=\textwidth]{Figs/lattice.pdf}
\caption{The lattice structure of $\precsim$.}
\label{Fig:PrecSim}
\end{center}
\end{figure*}
